phylo_analyses

### 2018-03-28 reports/phylo_report.rmd
getting rid of "exploiter" terminology and just sticking with median.

subset the tree
```{r}
  tree_plotting<-drop.tip(aus_bird_tree,aus_bird_tree$tip.label[!aus_bird_tree$tip.label%in%row.names(trait)])
  response_variables$SCIENTIFIC_NAME<-gsub(" ","_",response_variables$SCIENTIFIC_NAME)
  rv<-filter(response_variables,SCIENTIFIC_NAME%in%tree_plotting$tip.label)
  exploiter<-as.array(rv$exploiter) #the median
  row.names(exploiter)<-rv$SCIENTIFIC_NAME
  exploiter2<-exploiter-mean(exploiter)

  tree_plotting_2<-drop.tip(tree_plotting,tree_plotting$tip.label[!tree_plotting$tip.label%in%row.names(exploiter2)])
  trait<-subset(trait,row.names(trait)%in%tree_plotting_2$tip.label)
  dd<-data.frame(urb=exploiter2)
```

>>>>

subset the tree
```{r}
  tree_plotting<-drop.tip(aus_bird_tree,aus_bird_tree$tip.label[!aus_bird_tree$tip.label%in%row.names(trait)])
  response_variables$SCIENTIFIC_NAME<-gsub(" ","_",response_variables$SCIENTIFIC_NAME)
  rv<-filter(response_variables,SCIENTIFIC_NAME%in%tree_plotting$tip.label)
  median_rv<-as.array(rv$urban_median)
  row.names(median_rv)<-rv$SCIENTIFIC_NAME
  median_rv2<-median_rv-mean(median_rv)

  tree_plotting_2<-drop.tip(tree_plotting,tree_plotting$tip.label[!tree_plotting$tip.label%in%row.names(median_rv2)])
  trait<-subset(trait,row.names(trait)%in%tree_plotting_2$tip.label)

  dd <- data.frame(urb=median_rv2)
